### 2024-03-23 src/data_prep/data_prep.Rmd
added descriptives to data_prepRMD and fixed a bit of the descriptives structure

## starting with out DV: ratings
```{r Raw DV print, echo=FALSE}
print(summary(movie_data$averageRating))
```

Okay. So the scale is okay BUT remember that these are AVERAGE ratings, and that on average ratings 1 and 10 are quite extreme and frankly, unrealistic.

@@

```{r include=FALSE, paged.print=TRUE}
movie_data <- movie_data %>%
  filter(numVotes > 100) 
```

@@

@@

```

@@

movie_data %>%
  group_by(slide_window_5) %>%
  count()
```

@@

```{r include=FALSE}
movie_data <- movie_data %>%
  mutate(genre_dummy = 1) %>%
  pivot_wider(names_from = genres, values_from = genre_dummy, values_fill = list(genre_dummy = 0)) %>%
   rename(
    scifi = `sci-fi`,
    filmnoir = `film-noir`,
    gameshow = `game-show`,
    realitytv = `reality-tv`,
    talkshow = `talk-show`
  )
```

>>>>

## starting with out DV: ratings variable are defined as averageRating and should be between 1 and 10.
```{r Raw DV print, echo=FALSE}
print(summary(movie_data$averageRating))
```

The mean of the averageRating variable is 6.6.

```{r DV scale, echo=FALSE}
Okay. So the scale is okay BUT remember that these are AVERAGE ratings, and that on average ratings 1 and 10 are quite extreme and frankly, unrealistic.

@@

```{r include=FALSE, paged.print=TRUE}
movie_data <- movie_data %>%
  filter(numVotes > 100) 
```
Now that we have filtered the number of votes of each film to be more than 100, Films now have on average 24500 votes.

@@

We also have created a dummy variable called above_avg which indicates whether a film has a rating above or below average.

@@

```
After filtering to only series and movies, we end up with 120273 movies and 27722 series.

@@

movie_data %>%
  group_by(slide_window_5) %>%
  count()
```
We have filtered the data set to only include movies and series that have been released after 1925.

@@

```{r include=FALSE}
movie_data <- movie_data %>%
  mutate(genre_dummy = 1) %>%
  pivot_wider(names_from = genres, values_from = genre_dummy, values_fill = list(genre_dummy = 0)) %>%
   rename(
    scifi = `sci-fi`,
    filmnoir = `film-noir`,
    gameshow = `game-show`,
    realitytv = `reality-tv`,
    talkshow = `talk-show`
  )
```
After all the filtering, we have 70087 films left in our data set. From this number, 60246 are movies and 9841 are series. The resulting standard deviation for the total of films is 1.12. 
In the period from 2015 until 2019, the most amount of films were released being 11353, 2019 was the year with the biggest amount of releases, 2586 films. On the other hand, 1926 the least amount of films were released on IMDB, 54 films. 
The average number of votes in the final dataset was 7146.
In terms of runtime, the films are on average 101 minutes long.
The average ratings of the films in our final data set is 6.3, the lowest rating noted as 1 and the highest as 10.
